Feasibility of Harvesting Power To Run A Domestic Water Meter Using Streaming Cell Technology

### 2014-10-03 paper.tex
Start estimating harvester size

    Based on the pressure applied and the flow rate through the cell, the input power is \SI{539}{\milli\watt}.
    Energy conversion efficiency is in the order of $1\times 10^{-6}\%$.

@@

    % \section{Estimation of Streaming Cell Harvester}
    % \label{sect:harvesterSize}

    \section{Conclusion}
    \label{sect:conclusion}
    We have calculated approximately \SI{1}{\kilo\joule} of energy is dissipated per day inside a typical water meter at a two occupant dwelling.
    We have estimated that a harvester would need to harvest approximately \SI{10}{\joule} of energy per day to record and transmit water consumption data.
    Therefore an energy harvester with an energy conversion efficiency of 1\% is required.
    Streaming cells we constructed produced conversion efficiencies in the order of $1\times 10^{-6}\%$.

>>>>

    Based on the pressure applied and the flow rate through the cell, the input power is \SI{539}{\milli\watt}.
    Energy conversion efficiency is in the order of $1\times 10^{-6}\%$.
    While the conversion efficiency is much lower than those stated in the introduction, we use much larger channel dimensions and use tap water as our working fluid.

@@

    \section{Sizing of Streaming Cell Harvester}
    \label{sect:harvesterSize}
    In order to achieve the target conversion efficiency of 1\% the internal channel height must be reduced to something in the order of \SI{1}{\micro\meter}--\SI{10}{\nano\meter}.

    \section{Conclusion}
    \label{sect:conclusion}
    Approximately \SI{1}{\kilo\joule} of energy is dissipated per day inside a typical water meter at a two occupant dwelling.
    We have estimated that a harvester would need to harvest approximately \SI{10}{\joule} of energy per day to record and transmit water consumption data.
    Therefore an energy harvester with an energy conversion efficiency of 1\% is required.
    Streaming cells we constructed produced conversion efficiencies in the order of $1\times 10^{-6}\%$.
